Appendix

### 2021-11-29 writing/Manuscript_June2021.Rmd
work in progress, second pass through results/start of discussion

We found steady changes in the recognizability of children's drawings as a function of age (Figure \ref{fig:main-results}), replicating prior work with an observational dataset collected at a free-standing kiosk [@long2021parallel]. 
Moreover, we found that this age-related change did not depend on the drawing task children completed: Children's drawings were just as recognizable when they were cued with a photograph ("Draw this rabbit as it looks in the picture") as when they were cued with the category label ("Can you draw a rabbit?").  
While we thought that older children might produce more recognizable drawings when cued with a photograph of a highly prototypical exemplar based on prior work with adult participants [@yang2021visual], we did not find evidence of an interaction between age and cue type. 
However, we did observe a main effect of geographical site: children in Beijing, China producde more recognizable drawings than children in San Jose, USA (Table 1). A closer look comparing the recognizability of the drawings made by children at each age and site hints that the children in the Beijing group produced more recognizable drawings earlier in development.

In follow-up analyses, we aimed to understand the nature of this difference in recognizability across sites. 
We initially hypothesized that any differences in drawing recognizability between sites would be mediated by the amount of effort children expended while drawing or their tracing abilities. 
Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.  
We found that children spent more time drawing when prompted with a picture cue than a verbal cue, and that children in the Beijing group spent more time on their drawings than their counterparts in San Jose. 
By contrast, children's tracing abilities did not vary across geographical sites: Figure \ref{fig:tracing} shows the average tracing score at each age at each site. While children's tracing abilities increased steadily with age, as in prior work [@long2021parallel], children from both sites produced equally good tracings.

@@

# General Discussion
Here we examined the developmental trajectory of the recognizability of children's drawings across two different drawing tasks and geographical locations. Overall, we found a consistent developmental trajectory from 4-9 years of age, replicating previous work using observational datasets [@long2021parallel]. We found that asking children to draw categories when provided with a verbal cue ("Can you draw a [cat]?") vs. a picture cue ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced. While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bremmer1984prior], this did not seem to change how recognizable their drawings were to outside observers. Thus, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall specific, canonical exemplars of object categories when they are trying to draw them.

>>>>

We found steady changes in the recognizability of children's drawings as a function of age (Figure \ref{fig:main-results}), replicating prior work using the verbal-cue paradigm under less controlled settings [@long2021parallel]. 
Moreover, we found that this age-related change did not depend on the drawing task children completed: Children's drawings were just as recognizable when they were cued with a photograph ("Draw this rabbit as it looks in the picture") as when they were cued with the category label ("Can you draw a rabbit?").  
While we thought that older children might produce more recognizable drawings when cued with a photograph of a highly prototypical exemplar, as adult participants do [@yang2021visual], we did not find evidence of an interaction between age and cue type. 
However, we did observe a main effect of geographical site: children in Beijing, China produced drawings that were more recognizable than children in San Jose, USA (Table 1), reflecting steeper age-related gains earlier in development.

In follow-up analyses, we investigated potential sources of variation that might explain these site-related differences. 
We initially hypothesized that any differences in drawing recognizability between sites would be mediated by the amount of effort children expended while drawing or their tracing abilities. 
Figure \ref{fig:effort-covariates} shows three effort covariates -- average intensity, number of strokes used, and time spent drawing -- measured for each drawing as a function of children's age, drawing task, and geographical site.  
We found that children spent more time drawing when prompted with a picture cue than a verbal cue, and that children in the Beijing group spent more time on their drawings than their counterparts in San Jose. 
By contrast, children's tracing abilities did not vary across geographical sites: Figure \ref{fig:tracing} shows the average tracing score at each age at each site. While children's tracing abilities increased steadily with age, as in prior work [@long2021parallel], children from both sites produced equally good tracings.

@@

# General Discussion
Here we examined developmental change in children's ability to produce recognizable drawings of familiar object concepts and potential variation in task performance due to demands on memory. 
We found steady improvement from 4-9 years of age in two groups of children tested in different sites, replicating prior work [@long2021parallel].

We found that asking children to draw categories when provided with a verbal cue ("Can you draw a [cat]?") vs. a picture cue ("Can you draw this [cat] as it looks in the picture?") had little effect on the recognizability of the drawings that children produced. While older children may have integrated specific visual information that was present in the photographs, in keeping with prior work [@bremmer1984prior], this did not seem to change how recognizable their drawings were to outside observers. Thus, these results suggest that younger children's drawings are unlikely to be constrained by their ability to recall category-diagnostic visual features when they are trying to draw them.
